### 2015-03-04 ThesisJo/derivations.tex
la2pdf commit - 2015:02:03	12:29:14	(Tue 3.Feb)
la2pdf commit - 2015:02:03	14:24:40	(Tue 3.Feb)
la2pdf commit - 2015:02:26	14:27:18	(Thu26.Feb)
la2pdf commit - 2015:03:04	14:13:58	(Wed 4.Mar)

\begin{align}
\nabla\cdot(-\nabla s') &= \nabla\cdot\Big(\rho_0 \frac{\partial\v'}{\partial t}\Big) &
\frac{\partial}{\partial t}\frac{\partial\rho'}{\partial t} &= \frac{\partial}{\partial t}\Big(-\rho_0\nabla \cdot \v'\Big)\nn
-\nabla^2 s' &= \rho_0 \nabla\cdot\frac{\partial\v'}{\partial t} &
\frac{\partial^2\rho'}{\partial t^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} = -\rho_0\nabla\cdot\frac{\partial \v'}{\partial t}
\end{align}
%
and we can now see that
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = 0.
\end{align}
%
This is called the homogeneous lossless wave equation, because there is no source term. The inhomogeneous equation can be obtained in a similar way, by altering the linearized continuity equation to:
%
\begin{align}
\frac{\partial\rho'}{\partial t} &= -\rho_0\nabla \cdot \v' - \rho_0f(\p,t). \label{wave_eq_mass_conservation_source}
\end{align}
%
where $\rho_0f(\p,t)$ is the rate of mass change (in $\left[\frac{\text{kg}}{\text{m}^3\text{s}}\right]$) caused by the source. Following the exact same procedure as before we obtain:
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = \rho_0\frac{\partial f(\p,t)}{\partial t}.
\end{align}
%

@@

Let $\X[n]$ be the data received by an array, pre-steered to all pixels in the image, and $\w$ be the window applied to these spatial data. Then we defined the beamformer output $z$ as the weighted sum of the data:
%
\begin{align}
z[\w,n] = \w\H\X[n] = \sumb{m=0}{M-1} w_m x_m^*[n]
\end{align}
%
From a set of $P$ windows the LCA beamformer selects the window $p$ that yield the least output power:
%
\begin{align}
\argmin{p}{E\big\{|z|^2\big\}} = \argmin{p}{E\big\{|\w_p\H\X[n]|^2\big\}} \qquad\text{subject to}\qquad \w\H\a = 1
\end{align}

>>>>

\begin{align}
\nabla\cdot(-\nabla s') &= \nabla\cdot\Big(\rho_0 \frac{\partial\v'}{\partial t}\Big) &
\frac{\partial}{\partial t}\frac{\partial\rho'}{\partial t} &= \frac{\partial}{\partial t}\Big(-\rho_0\nabla \cdot \v'\Big)\nn
-\nabla^2 s' &= \rho_0 \nabla\cdot\frac{\partial\v'}{\partial t} &
\frac{\partial^2\rho'}{\partial t^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} = -\rho_0\nabla\cdot\frac{\partial \v'}{\partial t}
\end{align}
%
and we can now see that
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = 0.
\end{align}
%
This is called the homogeneous lossless wave equation, because there is no source term. When our signal $s$ signifies pressure (N/m$^2$), this links time and space by means of mass flow rate (kg/(m$^3$s). The inhomogeneous equation can be obtained in a similar way, by altering the linearized continuity equation to include a source:
%
\begin{align}
\frac{\partial\rho'}{\partial t} &= -\rho_0\nabla \cdot \v' - \rho_0f(\p,t). \label{wave_eq_mass_conservation_source}
\end{align}
%
where $\rho_0f(\p,t)$ is the rate of mass change (in $\left[\frac{\text{kg}}{\text{m}^3\text{s}}\right]$) caused by the source. Following the exact same procedure as before we obtain:
%
\begin{align}
\nabla^2 s' - \frac{1}{c^2}\frac{\partial^2 s'}{\partial t^2} = \rho_0\frac{\partial f(\p,t)}{\partial t}.
\end{align}
%

@@

Let $\X[n]$ be the data received by an array, pre-steered to all pixels in the image, and $\w$ be the window applied to these spatial data. Then we defined the beamformer output $z$ as the weighted sum of the data:
%
\begin{align}
z[\w,n] = \w\H\X[n] = \sumb{m=0}{M-1} w_m x_m^*[n]
\end{align}
%
From a set of $P$ windows the LCA beamformer selects the window $p$ that yield the least output power:
%
\begin{align}
\argmin{p}{E\big\{|z|^2\big\}} = \argmin{p}{E\big\{|\w_p\H\X[n]|^2\big\}} \qquad\text{subject to}\qquad \w\H\a = 1
\end{align}
%
We can estimate $E\big\{|\w_p\H\X[n]|^2\big\}$ as
%
\begin{align*}
\sigma^2_{z_p}[n] = \frac{1}{N_k} \sumb{n'=n-K}{n+K} | z_p[n'] |^2
\end{align*}
%
To add some extra flexibility, we can also estimate the variance by a weighted combination of local pixels
%
\begin{align*}
\sigma^2_{z_p}[x,n] = \frac{1}{N_x N_k} \sumb{x'=x-X}{x+X} \sumb{n=n-K}{n+K} w_\text{prf}[x',n']\big| z_p[x',n'] \big|^2
\end{align*}
%
where $w_\text{prf}[x',n']$ is a normalized 2 dimensional weight function.

Kaiser:
%
\begin{align*}
w[n] = \frac{I_0\big( \pi\alpha\sqrt{1-(\frac{2n}{N-1}-1)^2}\big)}{I_0(\pi\alpha)}
\end{align*}
%
where $I_0$ is a zeroth order modified Bessel function of the first kind.
